Adaptative neighbouring methods applied to telephonic base stations

### 2024-09-03 article.tex
Retrait des crochets

    \subsection{Additional database}
        In order to compare the results of city detection, a reference database was needed. We therefore used the population data provided by INSEE.
        [Pas sûr de l'utilité de présenter cette base en fait, ptet juste la principale suffit]

@@

        \subsubsection{Angle criterion}
            Let $p$, $q$, $r$ be three BS of $P$, where $q$ and $r$ are $p$'s potential neighbours. As said before, coverage areas of BS are limited by physics, this also implies that $r$ can be \og hidden\fg{} from $p$ by $q$ because $q$ is between $p$ and $r$ [trouver qqch pour prouver ce que je dis].

>>>>

    \subsection{Additional database}
        In order to compare the results of city detection, a reference database was needed. We therefore used the population data provided by INSEE.

@@

        \subsubsection{Angle criterion}
            Let $p$, $q$, $r$ be three BS of $P$, where $q$ and $r$ are $p$'s potential neighbours. As said before, coverage areas of BS are limited by physics, this also implies that $r$ can be \og hidden\fg{} from $p$ by $q$ because $q$ is between $p$ and $r$.
